---
title: "CW3_coding"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
getwd()
```

## Slide with Plot

```{r pressure}
help(nhanes)
```


```{r}
require(mice)
cc(nhanes)
summary(nhanes)
nrow(cc(nhanes))
md.pattern(nhanes)
library(mice)

```

```{r}
imps_normb <- mice(nhanes, printFlag = FALSE, seed = 1)

imps_normb$imp$bmi[,1]


```

```{r}
fits <- with(imps_normb, lm(bmi ~ age + hyp + chl))
class(fits)

fits$analyses[[1]]

summary(fits$analyses[[1]])

```

```{r}

ests <- pool(fits)
ests # look at riv and lambda
summary(ests, conf.int = TRUE)

```

```{r}
ests_seed2 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 2), lm(bmi ~ age + hyp + chl)))
ests_seed3 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 3), lm(bmi ~ age + hyp + chl)))
ests_seed4 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 4), lm(bmi ~ age + hyp + chl)))
ests_seed5 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 5), lm(bmi ~ age + hyp + chl)))
ests_seed6 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 6), lm(bmi ~ age + hyp + chl)))
```

```{r}
ests_seed2
ests_seed3
ests_seed4
ests_seed5
ests_seed6
```

```{r}
ests_seed1_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 1, m = 100), lm(bmi ~ age + hyp + chl)))
ests_seed2_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 2, m = 100), lm(bmi ~ age + hyp + chl)))
ests_seed3_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 3, m = 100), lm(bmi ~ age + hyp + chl)))
ests_seed4_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 4, m = 100), lm(bmi ~ age + hyp + chl)))
ests_seed5_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 5, m = 100), lm(bmi ~ age + hyp + chl)))
ests_seed6_100 <- pool(with(mice(nhanes, printFlag = FALSE, seed = 6, m = 100), lm(bmi ~ age + hyp + chl)))
```

```{r}
ests_seed1_100
ests_seed2_100
ests_seed3_100
ests_seed4_100
ests_seed5_100
ests_seed6_100
```

```{r}
# Q4

load("dataex4.Rdata")
imp0 <- mice(dataex4, maxit = 0)
imp0

```


```{r}
# beta0 <- 1.5
# beta1 <- 1
# beta2 <- 2
# beta3 <- 1
# 4 a
ests_q4_seed1 <- pool(with(mice(dataex4, printFlag = FALSE, maxit = 20,
                                seed = 1, m = 50), lm(y ~ x1 + x2 + (x1 * x2))  ))
ests_q4_seed1
summary(ests_q4_seed1, conf.int = TRUE)
```



```{r}
# 4 b
dataex4$x1x2 <- dataex4$x1 * dataex4$x2
imp0 <- mice(dataex4, maxit = 0)
meth <- imp0$method
meth["x1x2"] <- "~I(x1*x2)"
meth
pred <- imp0$predictorMatrix
pred[c("x1", "x2"), "x1x2"] <- 0
pred[, c("x1", "x2")] <- 0
pred["x1", "x2"] <- 1
pred["x2", "x1"] <- 1
pred

visSeq <- imp0$visitSequence
visSeq

ests_q4b_seed1 <- pool(with(mice(dataex4, method = meth,
                                 predictorMatrix = pred, maxit = 20,
                                 printFlag = FALSE, seed = 1, m = 50),
                            lm(y ~ x1 + x2 + (x1 * x2))  ))


ests_q4b_seed1
plot(mice(dataex4, method = meth, predictorMatrix = pred,
                                 printFlag = FALSE, seed = 1, m = 50),
     layout = c(6,6))
summary(ests_q4b_seed1, conf.int = TRUE)

```


```{r}
# dataex4$x1x2 <- dataex4$x1 * dataex4$x2

# If we impute the BMI directly, its values
# may be inconsistent with the imputed values of height and weight (none of the three variables is fully
# observed). Also, because there are cases where only one of these two variables is missing, to possibly gain
# some precision, we want to impute the height and the weight separately and BMI should then be calculated
# from the (imputed) values of these two variables. If BMI is not a relevant predictor in any of the other
# imputation models, we could just exclude BMI from the imputation and calculate it afterwards. To use BMI
# as a predictor in the other imputation models, it has to be calculated in each iteration of the algorithm,
# which in mice() is possible through the so-called passive imputation strategy, which requires us to specify a
# formula to calculate BMI through the I() operator.

ests_q4c_seed1 <- pool(with(mice(dataex4, maxit = 20,
                                 printFlag = FALSE, seed = 1, m = 50),
                            lm(y ~ x1 + x2 + (x1 * x2))  ))

summary(ests_q4c_seed1, conf.int = TRUE)

plot(mice(dataex4, printFlag = FALSE, seed = 1, m = 50), layout = c(6,6))

```


```{r}

# q 2

load("dataex2.Rdata")

data_range <- 1:100

for (i in data_range){
 # dataex2[, , i]
ests_q2_seed1 <- pool(with(mice(dataex2[, , i], method = "norm.nob",
                                 printFlag = FALSE, seed = 1, m = 20),
                            lm(Y ~ X)  ))
print(summary(ests_q2_seed1, conf.int = TRUE)[2, c(7, 8)])
}



```


```{r}


for (i in data_range){
 # dataex2[, , i]
ests_q2b_seed1 <- pool(with(mice(dataex2[, , i], method = "norm.boot",
                                 printFlag = FALSE, seed = 1, m = 20),
                            lm(Y ~ X)  ))
print(summary(ests_q2b_seed1, conf.int = TRUE)[2, c(7, 8)])
}



```



```{r}


# q5



```


```{r}



```


```{r}



```


```{r}



```











